\documentclass[11pt,a4paper]{article}
%\usepackage{multicol} % Include the multicol package
\usepackage{multicol}

\usepackage[utf8]{inputenc}
\usepackage[backend=biber]{biblatex} % or backend=bibtex

\usepackage{fontawesome} % Include the package at the beginning of your document
\usepackage[super]{nth}

\DefineBibliographyStrings{english}{url={\textsc{url}}}

%% Only needed if you want a Publication List
\addbibresource{own-bib.bib}

\usepackage[
left=1in,
right=1in,
top=1in,
bottom=1.25in,
headheight=26pt,
footskip=0.65in,
voffset=0.5cm
]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}



\pagestyle{fancy}
\fancyhf{}
\setlength{\headheight}{26pt} % Make sure this matches the geometry package headheight
\lhead{Iván Sepúlveda \\ \href{mailto:iesepulveda@outlook.com}{iesepulveda@outlook.com} \\+1-714-724-4958}
\rhead{\href{https://github.com/ivan-sepulveda//}{\faGithub\ github.com/ivan-sepulveda} \\ \href{https://www.yourLinkedinProfile.com/in/}{\faLinkedin\ linkedin.com/in/ivansepulveda/} \\ \ }


%%

\lfoot{Iván Sepúlveda}
\rfoot{Page \thepage\ of 2\\}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\setlength{\parindent}{0pt}

\newenvironment{myitemize}
{ \begin{itemize}[label={--}, leftmargin=*]
		\setlength{\itemsep}{0pt}
		\setlength{\parskip}{0pt}
		\setlength{\parsep}{0pt}     }
	{ \end{itemize}                  } 

\begin{document}
	
	
\section*{Education}
	\vspace{-8mm} % Adjust the value as needed to reduce the space above the line
	\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}
	\textbf{University of San Francisco} \hfill Graduated August 2019 \\
	Bachelor of Science - Physics \hfill Minors in Engineering \& Computer Science
	
		\vspace{-5mm} % Adjust the value as needed to reduce the space above the line
	
	\section*{Experience}
	\vspace{-3mm} % Adjust the value as needed to reduce the space above the line
	\hrule
	\vspace{3mm} % Adjust the value as needed to reduce the space above the line
	
	
	
	\subsection*{Aqua Finance, Inc. - Remote \hfill
			\vspace{-1mm} % Adjust the value as needed to reduce the space above the line
		 \normalfont{\textit{February 2026 - Present} } }
	\vspace{-1.5mm} % Adjust the value as needed to reduce the space above the line
	\textit{Manager of Analytics, Counterparty Risk}
	\vspace{-2.5mm} % Adjust the value as needed to reduce the space above the line
\begin{myitemize}
	\item Built counterparty risk frameworks, KPIs, early-warning indicators, predictive models, and dealer scorecards to monitor credit, fraud, operational, and compliance risk across dealers, applications, and sales channels.
	\item Led fraud detection and dealer monitoring initiatives using structured and unstructured data to identify abnormal activity, emerging risk trends, and escalation priorities.
	\item Defined monitoring rules, risk thresholds, alerts, and executive dashboards supporting proactive dealer oversight, portfolio health reviews, and risk-committee decision-making.
	\item Partnered cross-functionally with Credit, Sales, Underwriting, Product, Data, and Engineering teams to translate analytical findings into actionable risk controls and business recommendations.
\end{myitemize}
	
			\vspace{-6mm} % Adjust the value as needed to reduce the space above the line
	\subsection*{Forbright Bank - Remote \hfill
					\vspace{-1mm} % Adjust the value as needed to reduce the space above the line
		 \normalfont{\textit{September 2025 - February 2026} } }
	\vspace{-1.5mm} % Adjust the value as needed to reduce the space above the line
	\textit{Sr. Analyst - Servicing Analytics}
	\vspace{-2.5mm} % Adjust the value as needed to reduce the space above the line
\begin{myitemize}
	\item Delivered analytics, reporting, and strategic insights across Servicing, Collections, Capital Markets, Legal, and Compliance to monitor portfolio health and operations
	\item Analyzed repayment behavior and servicing trends; designed A/B tests and presented recommendations to leadership, clients, investors, and financial institutions
\end{myitemize}
		\vspace{-6mm} % Adjust the value as needed to reduce the space above the line
	\subsection*{Solar Mosaic LLC - Remote/Oakland, CA \hfill
	\vspace{-1mm}
	\normalfont{\textit{June 2021 - September 2025} } }
\vspace{-1.5mm}
\textit{Sr. Risk Analyst}
\vspace{-2.5mm}
\begin{myitemize}
	\item Developed SQL and Gephi-based network analysis using IP address, geographic, application, and business-registration data to identify relationships among connected entities.
\item Built an XGBoost classification model to estimate dealer offboarding risk across multiple prediction horizons, including 3-month, 6-month, and 12-month outcomes.
	\item Designed analytical datasets and feature pipelines in \texttt{Snowflake, DBT, Apache Airflow} and \texttt{Amazon Web Services} to support recurring risk monitoring and model development.
	\item Built dynamic partner risk scorecards combining model outputs, portfolio performance metrics, and early-warning indicators into structured monitoring frameworks.
	\item Conducted loan-level performance analysis across delinquency, repayment behavior, credit quality, and portfolio risk indicators to explain deviations from expected outcomes.
\end{myitemize}
		\vspace{-6mm} % Adjust the value as needed to reduce the space above the line
	\subsection*{L-Egant Solutions, LLC - Irvine, CA \hfill
					\vspace{-1mm} % Adjust the value as needed to reduce the space above the line
		 \normalfont{\textit{October 2019 - June 2021} } }
	\vspace{-1.5mm} % Adjust the value as needed to reduce the space above the line
	\textit{Lead Software Developer [Contract]}
	\vspace{-2.5mm} % Adjust the value as needed to reduce the space above the line
\begin{myitemize}
	\item Developed Python research software for a second-harmonic dispersion interferometer measuring 2D plasma-jet and gas-jet density profiles.
	\item Built experimental-control tools for camera configuration, shot-data collection, image capture, calibration workflows, and local data storage.
	\item Coauthored a peer-reviewed publication in Review of Scientific Instruments
	
\end{myitemize}
		\vspace{-6mm} % Adjust the value as needed to reduce the space above the line
	\subsection*{Mechanics Bank Auto Finance - Irvine, CA \hfill
					\vspace{-1mm} % Adjust the value as needed to reduce the space above the line
		 \normalfont{\textit{August 2019 - June 2021} } }
	\vspace{-1.5mm} % Adjust the value as needed to reduce the space above the line
	\textit{Data Analyst - Portfolio \& Servicing Risk}
	\vspace{-2.5mm} % Adjust the value as needed to reduce the space above the line
	\begin{myitemize}
		\item Used K-nearest neighbor analysis to compare high- and low-performing collections agents and evaluate patterns in collections behavior and outcomes.
		\item Built Random Forest models using Equifax, Experian, and TransUnion variables to identify credit-bureau attributes with the greatest lift in predicting delinquent loans.

\end{myitemize}
\vspace{-6mm} % Adjust the value as needed to reduce the space above the line
\subsection*{University of San Francisco - San Francisco, CA \hfill
\vspace{-1mm} % Adjust the value as needed to reduce the space above the line
\normalfont{\textit{May 2017 - August 2019} } }
\vspace{-1.5mm} % Adjust the value as needed to reduce the space above the line
\textit{Undergraduate Research Assistant — Plasma Modeling}
\vspace{-2.5mm} % Adjust the value as needed to reduce the space above the line
\begin{myitemize}
\item Developed a Monte Carlo simulation in Python to model electron transport through argon plasma, tracking particle position, energy, and collision events.
\item Delivered a research presentation explaining the simulation methodology and the role of plasma etching in modern semiconductor manufacturing.


	\end{myitemize}
		\vspace{-6mm} % Adjust the value as needed to reduce the space above the line
	
	
	
	\section*{Publications}
	\vspace{-3mm} % Adjust the value as needed to reduce the space above the line
	
	\hrule
	\vspace{2mm} % Adjust the value as needed to reduce the space above the line
	
	\input{publications}
	
		\vspace{-5mm} % Adjust the value as needed to reduce the space above the line
	
	\section*{Skills}
	\vspace{-1.5mm} % Adjust the value as needed to reduce the space above the line
\textit{Technical Skills}
\vspace{-2.5mm} % Adjust the value as needed to reduce the space above the line
	\begin{myitemize}
		\item Data Engineering \& Cloud: DBT, AWS, Snowflake, Docker, Airflow
		\item Programming \& Query Languages: Python, SQL, R, LaTeX, Java
		\item Scientific Computing \& Modeling: Pandas, NumPy, Spark, SciPy, Gephi
		\item Visualization \& Reporting: Tableau, Matplotlib, ggplot2, Mayavi, Streamlit, Plotly, Sigma
		\item Version Control \& Collaboration: Github, Bitbucket

		
	\end{myitemize}
	

	
	
	
\end{document}
